\documentclass[a4paper,10pt]{article}

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  PACKAGES
%%%%%%% --------------------------------------------------------------------------------------

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{csquotes}
\usepackage{tabularx}
\hypersetup{colorlinks=true,urlcolor=black}
\usepackage[11pt]{moresize}
\usepackage{setspace}
\usepackage{fontspec}
\usepackage[inline]{enumitem}
\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\usepackage{anyfontsize}
\usepackage{fontawesome5}
\usepackage{ragged2e}
\usepackage{expl3}

%%%% Set Margins
\usepackage[margin=1cm, top=1cm]{geometry}

%%%% Set Fonts
\setmainfont[
BoldFont=SourceSansPro-Semibold.otf,
ItalicFont=SourceSansPro-RegularIt.otf
]{SourceSansPro-Regular.otf}
\setsansfont{SourceSansPro-Semibold.otf}

%%%% Set Page
\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%%%% Set URL Style
\urlstyle{same}

%%%% Set Indentation
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%%%% Set Secondary Color
\definecolor{UI_blue}{RGB}{32, 64, 151}

%%%% Set Sections formatting
\titleformat{\section}{
\vspace{0.05cm}
\color{UI_blue} \raggedright \Large 
}{}{0em}{}[\vspace{-10pt} \hrulefill \vspace{-13pt}]

%%%% Set Subtext Formatting
\newcommand{\subtext}[1]{
#1\par\vspace{-0.12cm}}

\newcommand{\subtextit}[1]{
\vspace{0cm} 
\textit{ #1 
\vspace{-0.1cm}} }

%%%% Set Item Spacing
\setlist[itemize]{align=parleft,left=0pt..1em}

%%%% New Itemize "Zitemize" Formatting
\newenvironment{zitemize}{
\vspace{0.1cm}
\begin{itemize}\itemsep 1.5pt \parskip 2pt \parsep 5pt}
{\end{itemize}\vspace{-0.3cm}}

%%%% Define Skills Bold Formatting
\newcommand{\hskills}[1]{
\textbf{\bfseries #1} }

%%%% Metric placeholder — bright marker so unfilled numbers can't ship by accident.
\newcommand{\ph}[1]{{\color{red}\textbf{[#1]}}}

%%%% Set Subsection formatting
\titleformat{\subsection}{
\bfseries \fontsize{5cm}{30pt}
}{}{0em}{}[\vspace{-0.1cm}]

%%%% Set hyper link
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=UI_blue,
    pdftitle={Kexin Wei - CV for PhD},
    pdfpagemode=FullScreen,
    }

\begin{document}

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  HEADER
%%%%%%% --------------------------------------------------------------------------------------
\begin{center}
  \begin{center}
    {\Huge\color{UI_blue} Kexin Wei}
    \vspace{12pt}
    {\color{UI_blue} \hrule}
    \vspace{2pt}
    \vspace{2pt}
    \href{tel:+6589206264}{
      \raisebox{-0.05\height} \faPhone\ +65 89206264} ~ | ~
    \href{mailto:weikexin611@gmail.com}{
      \raisebox{-0.15\height} \faEnvelope\ weikexin611@gmail.com} ~ | ~
    \href{https://www.linkedin.com/in/kexin-wei-research/}{
      \raisebox{-0.15\height} \faLinkedin\ kexin-wei-research} ~ | ~
    \href{https://kexinwei.org/}{
      \raisebox{-0.15\height} \faGlobe\ kexinwei.org} ~ | ~
    \href{https://github.com/Kexin-Wei}{
      \raisebox{-0.15\height} \faGithub\ Kexin-Wei}
  \end{center}

\vspace{-0.15cm} 
% {\color{UI_blue} \hrulefill}
\end{center}

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  RESEARCH INTERESTS
%%%%%%% --------------------------------------------------------------------------------------
\section{Research Interests}
\begin{zitemize}
    \item \textbf{Robotics \& AI}: reinforcement learning for robot control and autonomy, medical and surgical robotics, and learning-based perception --- building on hands-on experience with 4/6-DoF robot arms, motion tracking, and deep-learning image segmentation.
    \item \textbf{Supporting background}: medical imaging, cyber-physical systems security, and full-stack engineering for research platforms.
\end{zitemize}

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  EDUCATION
%%%%%%% --------------------------------------------------------------------------------------
\section{Education}
\subsection*{\large M.Eng in Medical Robotics and AI \hfill Aug 2020 --- May 2022} 
\subtextit{National University of Singapore, Singapore \hfill GPA: 4.63/5.00}
\begin{zitemize}
    \item \textbf{Thesis}: Deep Reinforcement Learning (DRL) for Robot-assisted Surgical Training, which integrates DRL with a virtual laparoscopic surgery training system, wherein the DRL agent drives the surgical instrument and reaches goals of the surgical training tasks. \href{https://github.com/Kexin-Wei/Soft-tissue-deformation-in-laparoscopic-surgery-planning-with-DRL}{\faGithub~Code}.
    \item \textbf{Teaching Assistant}: ME2143E Motor Characteristics and ME5405 Machine Vision.
\end{zitemize}

\subsection*{\large B.Eng in Mechanical Design, Manufacture and its Automation \hfill Sep 2014 --- Jul 2019} 
\subtextit{Tongji University, China \hfill GPA: 4.61/5.00}
\begin{zitemize}
    \item \textbf{Final Project}: ECU Control of Boiler Combustion System with HMI Interface --- utilized a Freescale electric control unit receiving requests from a human interface, enabling users to monitor and control boiling procedures and components.
\end{zitemize}

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  RESEARCH EXPERIENCE
%%%%%%% --------------------------------------------------------------------------------------
\section{Professional Experience}

\subsection*{\large Research Engineer \hfill Mar 2025 --- Present}
\subtextit{Imperial Global Singapore (IGS) --- IN-CYPHER Programme with NTU \hfill Singapore}
\begin{zitemize}
    \item \textbf{Security research}: Investigating agentic, LLM-driven automated penetration testing (Autopatch) for medical cyber-physical systems, with PACS/DICOM assessment on an Orthanc/OHIF testbed --- contributing to a submitted platform paper.
    \item \textbf{Simulation}: Reproduced and validated a real-time closed-loop glucose-insulin simulator (OpenAPS/simglucose/UVA-Padova), translating MATLAB controllers to Python.
    \item \textbf{Research platform}: Built the evaluation platform end-to-end --- Flask + Vue.js visualization, Dockerized multi-container deployment, and lab compute (Ubuntu/RHEL, KVM) supporting group experiments.
\end{zitemize}

\subsection*{\large Software Team Lead \hfill Mar 2024 --- Jan 2025}
\subtextit{Creative Medtech Solutions Pte.Ltd. \hfill Singapore}
\begin{zitemize}
    \item \textbf{Robot}: Engineered robotics control systems including kinematics optimization for 4-DoF robot and control interfaces.
    \item \textbf{CyberSecurity}: Enhanced security through encryption protocols, SQL injection protection, and streamlined Qt-based GUI.
    \item \textbf{Image}: Developed 4D DICOM processing and US/MRI registration algorithms for medical image alignment.
    \item \textbf{Lead}: Led a team of 6 engineers, driving Git workflow standardization, Scrum adoption, GoogleTest integration, and code review standards.
\end{zitemize}

\subsection*{\large Research and Development Engineer \hfill Jun 2022 --- Mar 2024}
\subtextit{Creative Medtech Solutions Pte.Ltd. \hfill Singapore}
\begin{zitemize}
    \item \textbf{Robot}: Designed respiratory motion tracking algorithm for 6-DoF robot arm integrating an A*STAR CNN algorithm, verified in vivo across pig and dog trials.
    \item \textbf{AI}: Developed and validated an AI-based 3D medical image segmentation pipeline for prostate biopsy guidance.
    \item \textbf{Image}: Prototyped kidney segmentation solutions using SAM, MedSAM, and OpenCV for potential implementation.
    \item \textbf{Signal Processing}: Created power calibration algorithm for High Intensity Focused Ultrasound treatment, verified in ex-vivo experiments.
    \item \textbf{Sensor}: Integrated electromagnetic sensor system in HIFU treatment software for 3D visualization of the ultrasound probe.
    \item \textbf{Patent}: Filed 3 patents in medical algorithm design: HIFU calibration, respiratory tracking, and time synchronization.
\end{zitemize}

\subsection*{\large Research Assistant --- Internship \hfill Jul 2018 --- Sep 2018}
\subtextit{Beijing Surgerii Technology Co., Ltd. and Kii Lab of SJTU under Professor Kai Xu \hfill Shanghai, China}
\begin{zitemize}
    \item Conducted 20+ experiments to evaluate the three-dimensional positioning algorithm of a multi-backbone robot.
    \item Assembled and tested the motor-driven part of a surgical robot arm to ensure fundamental functions.
    \item Analyzed needle insertion experiment results and redesigned mechanical structure using AutoCAD for improved performance.
\end{zitemize}

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  PUBLICATIONS & PATENTS
%%%%%%% --------------------------------------------------------------------------------------
\section{Publications \& Patents}
\begin{zitemize}
    \item \textbf{K. Wei}, I. Zahid, L. Cheng, A. Bird, V. Schlegel, and N. Oliver, ``Generalisability of the Glucoprint: CGM-Based Re-identification Across Six Type~1 Diabetes Cohorts,'' Imperial College London / Imperial Global Singapore. \textit{In preparation}.
    \item L. Cheng, \textbf{K. Wei}, V. Schlegel, Q. Shao, A. Bird, W. Wei, N. Oliver, and A.A. Bharath, ``G-FM: Imputation-Guided Flow Matching for Multivariate Time-Series Generation,'' Imperial College London / Imperial Global Singapore. \textit{Submitted}.
    \item Y. Niu, Y. Ma, S. Nandakumar, M. Chen, V. Schlegel, \textbf{K. Wei}, L. Cheng, A. Bird, A.A. Bharath, and S.K. Lam, ``HealthLoopQA: A Context-Aware Question Answering Benchmark for Interpreting Wearable Monitoring Data in Diabetes Care,'' Imperial Global Singapore / Imperial College London / NTU. \textit{Submitted}.
    \item A.R. Bird$^\star$, V. Mohan$^\star$, \textbf{K. Wei}, Z. Cao, S.H. Ng, M.M. Mulay, V. Schlegel, M.G. Moffett, J.E. Moore Jr, C.-H. Chang, N. Oliver, and A.A. Bharath, ``Toward Trustworthy Closed-Loop Diabetes Technologies: A Dynamic Platform for Safety and Security Evaluation,'' Imperial Global Singapore / Imperial College London / NTU. \textit{Submitted}.
    \item \textbf{3 Patents Filed}: HIFU power calibration algorithm, robot respiratory tracking algorithm, and HIFU sweep mode time synchronization.
\end{zitemize}

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  AWARDS & HONORS
%%%%%%% --------------------------------------------------------------------------------------
\section{Awards \& Honors}
\begin{tabular}[t]{ p{11em} p{1em} p{43em}}
\hskills{AI} && Hackathon ``Runner Up" Prize at bio LLMs hosted by 4Catalyzer (2023) \\
\hskills{Mathematics Modeling} && 2nd Prize in CUMCM (2018); Honorable Mention in MCM/ICM (2018) \\
\hskills{Scholarship} && 3rd Class Award (2018); 1st Class Award (2016); 3rd Class Award (2015) \\
\end{tabular}

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  SKILLS
%%%%%%% --------------------------------------------------------------------------------------

\section{Skills}
\begin{tabular}{p{11em} p{1em} p{43em}}
\hskills{Programming} && Python, C++, Matlab, SQL, Rust\\
\hskills{Frameworks} && Qt, Flask, Vue.js, Flutter, OpenCV, VTK \\
\hskills{AI/ML} && PyTorch, TensorFlow, Claude Agent SDK, LangChain/LangGraph, OpenAI \& Gemini APIs\\
\hskills{Tools \& Infra} && Docker, Git, Linux (Ubuntu/RHEL), ROS, CI/CD \\
\hskills{Language} && English (C1), German (C1), Mandarin (native) \\
\end{tabular}

%%%%%%% --------------------------------------------------------------------------------------
%%%%%%%  COMMUNITY & SERVICE
%%%%%%% --------------------------------------------------------------------------------------
\section{Community \& Service}
\begin{zitemize}
    \item \textbf{Open source}: Contributor to Women Devs SG projects --- the community website (merged) and the \textit{bibsnbub} childcare-finder app.
    \item \textbf{Junior Developers SG}: Participant in coding dojos --- test-driven development, refactoring, and test automation.
    \item \textbf{Division Zero (div0)}: Cybersecurity workshops --- home-lab building, SHELLgym, and Hack Your First Flag.
\end{zitemize}

\end{document}